---
title: "World Happiness report 2021"
author: "Parnian Jahangiri Rad"
date: "2/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r,message=FALSE,warning=FALSE}
library(tidyverse)
library(janitor)
library(ggcorrplot)
library(caTools)
```

```{r}
data1 <- read_csv("world-happiness-report-2021.csv")
data1 <- data1 %>%
  clean_names()
```

```{r,message=FALSE,warning=FALSE}
#First 10 happiest countries(based on ladder_score):
data2 <- data1 %>%
  select(-starts_with("explained_by"))
#View(data2)
top_10 <- data2 %>%
  arrange(desc(ladder_score)) %>%
  head(10)

bottom_10 <- data2 %>%
  arrange(ladder_score) %>%
  head(10)
```

```{r}
ggplot(data = top_10,aes(x = reorder(country_name,ladder_score),
                         y = ladder_score,
                         fill = regional_indicator)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme(axis.title.y = element_blank())
  ggtitle("Top 10 happiest countries")
```

```{r}
ggplot(data = bottom_10,aes(x = reorder(country_name,ladder_score),
                         y = ladder_score,
                         fill = regional_indicator)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  ggtitle("Top 10 saddest countries")
```
  
### Find happiest regions  
```{r}
region_happiness <- data2 %>%
  group_by(regional_indicator) %>%
  summarise(mean(ladder_score))
```

```{r}
ggplot(data = region_happiness,
       aes(x = reorder(regional_indicator, `mean(ladder_score)`),
           y = `mean(ladder_score)`,
       fill = regional_indicator)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  xlab("") +
  ylab("") +
  ggtitle("Region Happiness")
```
  
### Relation between logged_gpd_per_capita and ladder_score    
```{r}
ggplot(data = data2 ,
       aes(x = logged_gdp_per_capita ,
           y = ladder_score)) +
  geom_point(aes(color = regional_indicator)) +
  ggtitle("Relation between logged_gpd_per_capita 
          and ladder_score")
```
  
increase in `logged_gpd_per_capita` increases `ladder_score`.  
  
There are 7 features which affects happiness based on `ladder_score`:  
- `log_gpd_per_capita`  
- `social_support`  
- `healthy_life_expendancy`  
- `freedom_to_make_life_choices`  
- `generosity`  
- `perceptions_of_corruption`  
- `dystopia_residual`  
  

```{r,message=FALSE,warning=FALSE}
#regional_data based on logged_gpd_per_capita
regional_data_gpd <- data2 %>%
  group_by(regional_indicator) %>%
  summarise(mean(logged_gdp_per_capita))
is.num <- sapply(regional_data_gpd,is.numeric)
regional_data_gpd[is.num] <- lapply(regional_data_gpd[is.num], round, 2)

ggplot(regional_data_gpd,aes(
        x = reorder(regional_indicator,`mean(logged_gdp_per_capita)`),
        y = `mean(logged_gdp_per_capita)`))+
        coord_flip()+
  geom_bar(stat="identity",fill="darkviolet") +
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
  ggtitle("Happiness of regional indicators based 
          on gpd_per_capita")
```
  
It seems that `logged_gdp_per_capita` has a high impact on ladder_score.(important feature).  
```{r,message=FALSE,warning=FALSE}
#regional_data based on social_support
regional_data_social_support <- data2 %>%
  group_by(regional_indicator) %>%
  summarise(mean(social_support))
is.num <- sapply(regional_data_social_support,is.numeric)
regional_data_social_support[is.num] <- lapply(regional_data_social_support[is.num], round, 2)

ggplot(regional_data_social_support,aes(
        x = reorder(regional_indicator,`mean(social_support)`),
        y = `mean(social_support)`))+
        coord_flip()+
  geom_bar(stat="identity",fill="magenta") +
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
  ggtitle("Happiness of regional indicators based 
          on social_support")
```
  
`social_support` seems to be an important feature as well. 
```{r,message=FALSE,warning=FALSE}
#regional_data based on healthy_life_expendancy
regional_data_healthy <- data2 %>%
  group_by(regional_indicator) %>%
  summarise(mean(healthy_life_expectancy))
is.num <- sapply(regional_data_healthy,is.numeric)
regional_data_healthy[is.num] <- lapply(regional_data_healthy[is.num], round, 2)

ggplot(regional_data_healthy,aes(
        x = reorder(regional_indicator,`mean(healthy_life_expectancy)`),
        y = `mean(healthy_life_expectancy)`))+
        coord_flip()+
  geom_bar(stat="identity",fill="violetred") +
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
  ggtitle("Happiness of regional indicators based 
          on healthy_life_expendancy")
```


Let's check out freedom_to_make_life_choices:  
```{r,message=FALSE,warning=FALSE}
#regional_data based on freedom_to_make_life choices
regional_data_freedom <- data2 %>%
  group_by(regional_indicator) %>%
  summarise(mean(freedom_to_make_life_choices))
is.num <- sapply(regional_data_freedom,is.numeric)
regional_data_freedom[is.num] <- lapply(regional_data_freedom[is.num], round, 2)

ggplot(regional_data_freedom,aes(
        x = reorder(regional_indicator,`mean(freedom_to_make_life_choices)`),
        y = `mean(freedom_to_make_life_choices)`))+
        coord_flip()+
  geom_bar(stat="identity",fill="cyan") +
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
  ggtitle("Happiness of regional indicators based 
          on freedom_to_make_life choices")
```
  
Interesting!!  

```{r,message=FALSE,warning=FALSE}
#regional_data based on generosity
regional_data_generosity <- data2 %>%
  group_by(regional_indicator) %>%
  summarise(mean(generosity))
is.num <- sapply(regional_data_generosity,is.numeric)
regional_data_generosity[is.num] <- lapply(regional_data_generosity[is.num], round, 2)

ggplot(regional_data_generosity,aes(
        x = reorder(regional_indicator,`mean(generosity)`),
        y = `mean(generosity)`))+
        coord_flip()+
  geom_bar(stat="identity",fill="blueviolet") +
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
  ggtitle("Happiness of regional indicators based 
          on generosity")
```

```{r,message=FALSE,warning=FALSE}
#regional_data based on perception_of_corruption
regional_data_perception <- data2 %>%
  group_by(regional_indicator) %>%
  summarise(mean(perceptions_of_corruption))
is.num <- sapply(regional_data_perception,is.numeric)
regional_data_perception[is.num] <- lapply(regional_data_perception[is.num], round, 2)

ggplot(regional_data_perception,aes(
        x = reorder(regional_indicator,`mean(perceptions_of_corruption)`),
        y = `mean(perceptions_of_corruption)`))+
        coord_flip()+
  geom_bar(stat="identity",fill="deeppink") +
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
  ggtitle("Happiness of regional indicators based 
          on perception_of_corruption")
```
  
```{r,message=FALSE,warning=FALSE}
#regional_data based on dystopia_residual
regional_data_dystopia <- data2 %>%
  group_by(regional_indicator) %>%
  summarise(mean(dystopia_residual))
is.num <- sapply(regional_data_dystopia,is.numeric)
regional_data_dystopia[is.num] <- lapply(regional_data_dystopia[is.num], round, 2)

ggplot(regional_data_dystopia,aes(
        x = reorder(regional_indicator,`mean(dystopia_residual)`),
        y = `mean(dystopia_residual)`))+
        coord_flip()+
  geom_bar(stat="identity",fill="lightslateblue") +
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
  ggtitle("Happiness of regional indicators based 
          on dystopia_residual")
```  
  
```{r,message=FALSE,warning=FALSE}
regional_mean_data <- inner_join(region_happiness,
  inner_join(regional_data_gpd,
  inner_join(regional_data_social_support,
  inner_join(regional_data_healthy,
  inner_join(regional_data_freedom,
  inner_join(regional_data_generosity,
  inner_join(regional_data_perception,
                                 regional_data_dystopia,
                                 by="regional_indicator"),
            by="regional_indicator"),
          by="regional_indicator"),
        by="regional_indicator"),
      by="regional_indicator"),
    by="regional_indicator"),
 by="regional_indicator") 
```
 
Feature importance using **correlation** (we will also plot it):  
```{r,message=FALSE,warning=FALSE}
cor(regional_mean_data$`mean(ladder_score)`,
    regional_mean_data$`mean(logged_gdp_per_capita)`)
```
 
```{r,message=FALSE,warning=FALSE} 
cor(regional_mean_data$`mean(ladder_score)`,
    regional_mean_data$`mean(social_support)`)
```
 
```{r,message=FALSE,warning=FALSE} 
names <- names(regional_mean_data)
names <- names[-c(1,2)]
y <- vector()
for(i in names){
  y <- append(y,
              cor(regional_mean_data$`mean(ladder_score)`,
                  regional_mean_data[[i]]))
}
y
```

```{r,message=FALSE,warning=FALSE}
df1 <- data.frame(names,y)
is.num <- sapply(regional_data_social_support,is.numeric)
df1[is.num] <- lapply(df1[is.num], round, 2)

ggplot(df1,aes(
        x = reorder(names,y),
        y = y)) +
        coord_flip() +
  geom_bar(stat="identity",fill="deepskyblue") +
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
  ggtitle("Feature importance using correlation")
```
  
### Pearson Correlation Matrix  
```{r}
cdf <- data2 %>%
  select(ladder_score,
         logged_gdp_per_capita,
         social_support,
         healthy_life_expectancy,
         freedom_to_make_life_choices,
         generosity,
         perceptions_of_corruption,
         dystopia_residual)

cor_df <- data.frame(cor(cdf))
ggcorrplot(cor_df, method ="square")
```
  
### Linear regression  
```{r}
set.seed(66)
split = sample.split(cdf$ladder_score, SplitRatio = 0.7)
training_set = subset(cdf, split == TRUE)
test_set = subset(cdf, split == FALSE)

lm_model <- lm(formula = ladder_score ~ ., data = training_set)
summary(lm_model)
```
```{r}
y_pred <- predict(lm_model, newdata = test_set)
pred_df <- as.data.frame(cbind(Prediction = y_pred , Actual = test_set$ladder_score))

ggplot(pred_df, aes(Actual, Prediction )) +
  geom_point() +
  theme_bw() +
  geom_abline() +
  labs(title = "Multiple linear regression" ,
       x = "real ladder_score",
       y = "predicted ladder_score")
```

### One-sample T-test  
East Asia as our sample  
```{r}
ea <- data2 %>%
  filter(regional_indicator == "East Asia")

ggplot(data = ea,aes(
  x = regional_indicator,
  y = ladder_score
      )) +
  geom_boxplot()
```

```{r}
t.test(ea$ladder_score, mu = 5)
```
